Block bootstrap consistency\\under weak assumptions

### 2017-03-14 Paper.tex

By construction, (see Equations~\eqref{eq:39} and~\eqref{eq:1})
\begin{equation}\label{eq:16}
  \tfrac{1}{\sqrt{n}} \sum_{t=1}^n (X_{nt}^{*} - \bar X_n)
  = \sum_{j=1}^{J_n} \Zb
\end{equation}
and
\begin{equation}\label{eq:17}
  \Em^{*}g(\Zb,\dots,\Zb[k]) = \frac{1}{n^{k-j+1}}
  \sum_{\tau_1=0}^{n-1} \cdots \sum_{\tau_{k-j+1}=0}^{n-1}
  g(Z_n(\tau_1, M_{nj}),\dots,Z_n(\tau_{k-j+1}, M_{nk}))
\end{equation}
almost surely for any function $g$ such that both
expressions are well-defined and any $j \leq k$. Equation~\eqref{eq:17}
conditions on the lengths of each block, but averages over their
starting points.

@@

\begin{proof}[Proof of Lemma~\ref{L1}]
  To prove part 1, take any positive number $x$. Then
  \begin{equation*}
    \pr\Big[\max_{i=1,\dots, \lfloor C n p_n \rfloor} M_{ni}/n \leq x \Big]
    = (1 - (1 - p_n)^{n x})^{\lfloor C n p_n \rfloor}
    = \exp(-C n p_n e^{-x n p_n}) \times (1 + o(1))
  \end{equation*}
  since $(1 - p_n)^{x/p_n} \to e^{-x}$. In addition, $n p_n e^{-n p_n} \to 0$
  by assumption, so
  \begin{align*}
    \pr\Big[\max_{i=1,\dots, \lfloor C n p_n \rfloor} M_{ni}/n \leq x \Big]
    \to \exp(0) = 1.
  \end{align*}
  Since $x$ is arbitrary, $\max_{i=1,\dots,\lfloor C n p_n \rfloor} M_{ni} / n \to^p 0$.

@@

\begin{lem}\label{L2}
  If $\{A_n\}$ is a sequence of events in $\Omega$ then the following
  are equivalent:
  \begin{align*}
  \pr[A_n] &\to 0, &
  \pr^*[A_n] &\to 0 \text{\ in\ }L_1, &
  &\text{and}&
  \Pm^*[A_n] &\to 0 \text{\ in\ }L_1.
  \end{align*}
\end{lem}
\begin{proof}
  Since $\pr[A_n] = \E |\pr^*[A_n]| = \E |\pr^*_{\mathcal{M}}[A_n]|$ these
  conditions are equivalent by definition.
\end{proof}

@@

\begin{lem}\label{L6}
  Under the conditions of Theorem~\ref{T1}, for any positive
  $\epsilon$ and $\epsilon'$ there exist constants $C_0$ and $n_0$
  such that
  \begin{multline}\label{eq:30}
    \pr \Big [ \sup_{\substack{\tau = 0,\dots,n-1 \\ m'=1,\dots,n}}
    \Em \Big ( \max_{ m = 1, \dots, m' } (n \, Z^*_n(\tau, m)^2 / m' ) \\
    \times \ind\Big\{\max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m' > C\Big\}\Big)
    > \epsilon \Big ] < \epsilon'
  \end{multline}
  for all $n > n_0$ and $C > C_0$.
  Moreover, the families of random variables \\
  $\{\max_{m=1,\dots,m'} Z^{*}_n(\tau, m)^2 n / m'; \tau, m', n\}$ and
  $\{Z^{*2}_{nj} n / M_{nj}; \tau, j, n\}$ are
  uniformly integrable for $n$ larger than some threshold $n_0$.
\end{lem}

>>>>

By construction, (see Equations~\eqref{eq:39} and~\eqref{eq:1})
\begin{equation}\label{eq:16}
  \tfrac{1}{\sqrt{n}} \sum_{t=1}^n (X_{nt}^{*} - \bar X_n)
  = \sum_{j=1}^{J_n} \Zb
\end{equation}
and
\begin{equation}\label{eq:17}
  \Em^{*}g(\Zb,\dots,\Zb[k]) = \frac{1}{n^{k-j+1}}
  \sum_{\tau_1=0}^{n-1} \cdots \sum_{\tau_{k-j+1}=0}^{n-1}
  g(Z_n(\tau_1, M_{nj}),\dots,Z_n(\tau_{k-j+1}, M_{nk}))
\end{equation}
almost surely for any function $g$ and any $j \leq k$. Equation~\eqref{eq:17}
conditions on the lengths of each block, but averages over their
starting points.

@@

\begin{proof}[Proof of Lemma~\ref{L1}]
  To prove part 1, observe that, for any increasing positive sequence
  $x_n$ such that $x_n p_n \to \infty$,
  \begin{equation*}
    \pr\Big[\max_{i=1,\dots, \lfloor C n p_n \rfloor} M_{ni} \leq x_n\Big] =
    (1 - (1 - p_n)^{x_n})^{\lfloor C n p_n \rfloor} \to \lim \exp(-C n p_n (1 - p_n)^{x_n})
  \end{equation*}
  and $C n p_n (1 - p_n)^{x_n} \to \lim C n p_n e^{-x_n p_n}$. Now, let
  $x_n = n x$ for any positive number $x$.  Then
  \begin{equation*}
    \pr\Big[\max_{i=1,\dots,\lfloor C n p_n \rfloor} M_{ni}/n \leq x \Big] \to
    \lim \exp(-C n p_n e^{-n p_n x}) =
    \exp(0) = 1.
  \end{equation*}
  Since $x$ is arbitrary, $\max_{i=1,\dots,\lfloor C n p_n \rfloor} M_{ni} / n \to^p 0$.

@@

\begin{lem}\label{L2}
  If $\{A_n\}$ is a sequence of events in $\Omega$ then the following
  are equivalent:
  \begin{align*}
  \pr[A_n] &\to 0, &
  \pr^*[A_n] &\to 0 \text{\ in\ }L_1, &
  &\text{and}&
  \Pm^*[A_n] &\to 0 \text{\ in\ }L_1.
  \end{align*}
\end{lem}
\begin{proof}
  Since $|\pr[A_n]| = \E |\pr^*[A_n]| = \E |\pr^*_{\mathcal{M}}[A_n]|$ these
  conditions are equivalent by definition.
\end{proof}

@@

\begin{lem}\label{L6}
  Under the conditions of Theorem~\ref{T1},
  \begin{multline}\label{eq:30}
    \lim_{C \to \infty} \limsup_{n \to \infty} \sup_{\substack{\tau = 0,\dots,n-1 \\ m'=1,\dots,n}}
    \E\Big(\max_{m = 1,\dots,m'} (n \, Z^*_n(\tau, m)^2 / m') \\
    \times \ind\Big\{\max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m' > C\Big\}\Big)
    = 0.
  \end{multline}
  Moreover, the families of random variables
  $\{\max_{m=1,\dots,m'} Z^{*}_n(\tau, m)^2 n / m'; \tau, m', n\}$ and
  $\{\max_{m=1,\dots,M_{nj}} Z^{*}_{nj}(u_{nj}, m)^2 n / M_{nj}; j, n\}$ are uniformly integrable.
\end{lem}
